Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-23 MS_thesis.tex
Rephrase acknowledgements

I am grateful to many friends who made the IISER journey enjoyable. Countless long days and nights with Adithyan, Abhishek, Arjun, Chebi, Gaurav, Harshit, Manas, Milie, and Shruthi, have greatly helped me grow as a person, both intellectually and emotionally. Arjun has always been a great sounding board for my thoughts, no matter how inane, and has been very patient and supportive in more ways than I could list here. Milie is the occasional fitness friend that everyone needs, and occasionally texting her encouraged me to hit the gym at least semi-regularly even during hectic parts of the thesis project when schedules were uncertain. I am indebted to our D\&D group in general and Manas in particular for introducing me to D\&D and Critical Role, both of which were very helpful in getting through the pandemic and the thesis year. Shruthi is a constant source of cat related mental health boosts and has more generally taught me a lot about a lot during my time at IISER. I am also grateful to Abhishek for letting me bother him with various physics-related questions throughout the project year. I entered this project as someone who knew some mathematics and some biology but quickly realized I would benefit from reading physics papers (typically written in physics language). Abhishek patiently answered all my basic questions about physics language/tools and skillfully helped me understand how physicists think. Insightful conversations about evolution with Gaurav were formative in gaining fresh perspectives on various topics. Closer to home, Akshay and Prerana have been my closest friends since high school and continue to provide unerring and unconditional love and support. I don't know where I would be without them today.

@@

%I would like to thank the KVPY fellowship program (now the INSPIRE program) by the Department of Science and Technology, Government of India, for providing me with financial support for the duration of my time at IISER. I would also like to thank the PARAM-Brahma facility at IISER Pune, part of the National Supercomputing Mission, Government of India, for providing me with computing resources, though I did not finally end up using the facility for this thesis.

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting accepted by an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices, both small and large; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages

>>>>

I am grateful to many friends who made the IISER journey enjoyable. Countless long days and nights with Adithyan, Abhishek, Arjun, Chebi, Gaurav, Harshit, Manas, Milie, and Shruthi, have greatly helped me grow as a person, both intellectually and emotionally. Arjun has always been a great sounding board for my thoughts, no matter how inane, and has been very patient and supportive in more ways than I could list here. Milie is the occasional fitness friend that everyone needs, and occasionally texting her encouraged me to hit the gym at least semi-regularly even during hectic parts of the thesis project when schedules were uncertain. I am indebted to our D\&D group in general and Manas in particular for introducing me to D\&D and Critical Role, both of which were very helpful in getting through the pandemic and the thesis year. Shruthi is a constant source of cat related mental health boosts and has more generally taught me a lot about a lot during my time at IISER. I entered this project as someone who knew some mathematics and some biology but quickly realized I would benefit from reading physics papers (typically written in physics language) --- Abhishek always enthusiastically responded to my annoying physics-related questions and patiently explained physics language to me throughout the project year, and for that I am grateful. Insightful conversations about evolution with Gaurav were helpful in gaining fresh perspectives on various topics. Closer to home, Akshay and Prerana have been my closest friends since high school and continue to provide unerring and unconditional love and support. I don't know where I would be without them today.

@@

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting accepted by an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices, both small and large.
}
\allowdisplaybreaks %allow align envts to go across pages
